---
title: "association rules"
author: "Aurelia"
date: "23/01/2021"
output: html_document
---

```{r}
#INSTALL LIBRARIES
install.packages('dplyr')
library(dplyr)
library(tidyr)
install.packages("data.table")
install.packages('lubridate')
library(lubridate)
install.packages("tidyverse")



```
```{r}
#INSTALL LIBRARIES
install.packages('dplyr')
library(dplyr)
library(tidyr)
library(data.table)
library(lubridate)
library(tidyverse)




```

```{r}
df = read_csv("http://bit.ly/SupermarketDatasetII")
```
```{r}
# View sample supermarket data on which we will run association rules
head(df)
```


```{r}
# Data dimensions 
dim(df)
```
there are 7500 rows and 20 columns

```{r}
#Structure 
str(df)
```
```{r}
summary(df)
```

```{r}
# Checking for Missing Values per column

colSums(is.na(df))
```

```{r}
# Checking for missing for the whole dataset
sum(is.na(df))
```


```{r}
anyDuplicated(df)
```


```{r}
install.packages("arules")
```

```{r}
library(arules)
```

```{r}
# Verifying the object's class
 
class(df)
```
```{r}
# Previewing our first 6 transactions
#
head(df)
```

```{r}

# Displaying top 15 most common items in the  dataset 

transact <- as(df, "transactions") 
# plot item frequency
itemFrequencyPlot(transact,topN=15,type="absolute")
```
```{r}
# Producing a chart of frequencies  

# ---
# Displaying top 15 most common items in the  dataset 

# 
par(mfrow = c(1, 2))

# plot the frequency of items
itemFrequencyPlot(transact, topN = 15,col="pink")

```
```{r}
# Building a model based on association rules 
# using the apriori function 
rules <- apriori(df, parameter = list(supp = 0.4, conf = 0.7,target = "rules",minlen=2))
```

```{r}
summary(rules)
```
Using  support levels of 0.4 and confidence level of 0.7 no rules were generated,will test with support of 0.001 and confidence level of 0.8
```{r}
rules1<- apriori(df, parameter = list(supp = 0.001, conf = 0.8,target = "rules",minlen=2))
```




```{r}
summary(rules1)
```
35 rules were obtained,this indicates that different levels of support and confidence matters when it comes to association mining
```{r}
# observing first 15  model rules
inspect(rules1[1:15])
```

```{r}
rules<-sort(rules, by="confidence", decreasing=TRUE)
inspect(rules1[1:15])
```

it is observed that someone who buys olive oil has a 100% chance of buying cottage cheese and milk