---
title: "SUPERMARKET 1"
author: "Aurelia"
date: "23/01/2021"
output:
  html_document: default
  word_document: default
---

```{r}
#INSTALL LIBRARIES
install.packages('dplyr')
library(dplyr)
library(tidyr)
install.packages("datatable")
install.packages('lubridate')
library(lubridate)

install.packages("rtools")
install.packages("DataExplorer") 
install.packages("Hmisc") 
install.packages("pastecs")

install.packages("corrplot") 

install.packages("caret")
```


```{r}
library("data.table") 


library(tidyverse) 

library(warn = -1) 

library(ggplot2) 
library(lattice)
library(corrplot) 
library(DataExplorer) 











library(magrittr) 
```
```{r}
# loading the dataset

df = read_csv('http://bit.ly/CarreFourDataset')
```

```{r}
# Checking the top observations

head(df)
```

```{r}
# Checking the bottom observations

tail(df)
```

```{r}
# Viewing the structure of the dataset
# ---
#
str(df)
```
```{r}
# Viewing the statistical summary of the dataset
# ---
# 
summary(df)
```

```{r}
# Viewing the dimension of  dataset
dim(df)
```
There are 1000 rows and 16 columns

# Data cleaning

```{r}
# Checking for Missing Values per column

colSums(is.na(df))
```
```{r}
# Checking for missing for the whole dataset
sum(is.na(df))
```
there are no misssing values

```{r}
# different ways of visualizing missing data

plot_missing(df)
```
```{r}
install.packages("naniar")
library(naniar)
gg_miss_var(df)
```

```{r}
#look out for duplicates

anyDuplicated(df)
```
there are no duplicates
```{r}
df_num<-select_if(df, is.numeric)
df_num
```

```{r}
boxplot(df_num$Quantity,col = "pink",main = "Quantity",border = "brown",xlab="quanutity",horizontal = T)
```
```{r}
boxplot(df_num$Tax,col = "pink",main = "Tax",border = "brown",xlab="tax",horizontal = T)
```
```{r}
boxplot(df_num$Rating,col = "pink",main = "Rating",border = "brown",xlab="Rating",horizontal = T)
```
```{r}
boxplot(df_num$Total,col = "pink",main = "Total",border = "brown",xlab="Total",horizontal = T)
```
```{r}
# Checking the column names
names(df)
# Replacing spaces in the columns names with an underscore
names(df) <- gsub(" ", "_", names(df))
# Confirming the columns names have changed
names(df)
```


```{r}
#checking numeric variables after change of column names
df_numeric<-select_if(df, is.numeric)
df_numeric
```


```{r}
# Identify the columns with zero column variance.
names(df_numeric[, sapply(df_numeric, function(v) var(v, na.rm=TRUE)==0)])
```

```{r}
# Drop the columns as they result to error "stop("cannot rescale a constant/zero column to unit variance")" 
df_new <- subset(df_numeric, select = -c(gross_margin_percentage))
```



```{r}
df.pca <- prcomp(df_new, center = TRUE, scale. = TRUE)
summary(df.pca)
```

The first component(PC1) contributes 70.31% of the important data,pc2 contributes 14.29% etc

```{r}
plot(df.pca,type="l")
```

```{r}
str(df.pca)
```





```{r}
supermarket =cbind(df_new,df.pca$x[,1:2])
head(supermarket)
```



```{r}
summary(df.pca)
```
```{r}
install.packages("factoextra")
library(factoextra)
```
```{r}
fviz_eig(df.pca)
```


Shows the percentage of variances explained by each principal component


```{r}
fviz_pca_ind(df.pca,
             col.ind = "cos2", # Color by the quality of representation
             gradient.cols = c("red", "green"),
             repel = TRUE     # Avoid text overlapping
             )
```

Individuals with a similar profile are grouped together.


```{r}
fviz_pca_var(df.pca,
             col.var = "contrib", # Color by contributions to the PC
             gradient.cols = c("red", "green"),
             repel = TRUE     # Avoid text overlapping
             )
```
Graph of variables. Positive correlated variables point to the same side of the plot. Negative correlated variables point to opposite sides of the graph.



```{r}

fviz_pca_biplot(df.pca, repel = TRUE,
                col.var = "red", # Variables color
                col.ind = "green"  # Individuals color
                )
```


Biplot of individuals and variables













